Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-01 doc/main_jfm.tex
working on shear examples

The centroid of the pre-relaxed $58$-body Janus vesicle is initially
placed at the origin and the shear flow with a certain shear rate $\chi$
is applied. Snapshots of the JP vesicle in a shear flow with a shear
rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
show the initial shape obtained from the relaxation run and the deformed
configurations of the JP vesicle at time $t=4000$ are in panels (c)
and (d). The background color in panels (a) and (c) is the strength of
the action of the hydrophobic attraction. Red corresponds to a strong
action while blue is weak action. The hydrophobic layer clearly has the
strongest action. To demonstrate the tank-treading behavior of the
vesicle, panels (b) and (d) provide the streamlines of the fluid
velocity around the JP vesicle. In panel (d), we can clearly observe
the clockwise tank-treading motion.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow
  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
  JP vesicle where black arrows are the particle orientations. (b)
  The particle velocities and streamlines of the configuration in (a).
  Streamlines are plotted in the background as solid curves. Red arrows
  represent the particle velocities. (c) Deformed JP vesicle at
  $t=4000$. At this configuration the JP vesicle is tank-treading.
  (d) The particle velocities and streamlines of the configuration in
  (c). The background colors in panels (a) and (c) represent the
  strength of the hydrophobic attraction potential. The blue region
  shows no action and the red region in the bilayer gives the strongest
  action.}
\end{figure}
%
%

To extract additional physical properties of the proposed model, we
compute the total length, reduced area, and excess length of the bilayer
structure. The enclosed area and the total length of the structure are
calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
where $A$ the area, and $L$ the total length of the JP vesicle, and
the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
Figure~\ref{figure4} shows these quantities for a JP vesicle
suspended in a shear flow with shear rates
$\chi=\{0.002,0.0025,0.003,0.0035\}$. Since the starting configuration
is nearly circular, the reduced area decreases from an initial value
close to $1$. The smooth curves in panel (a) are best fits of the
exponential model $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the
decay rate $k$ is independent of the shear rate for sufficiently large
shear rates, and the terminal reduced areas of each case are shown in
the inset. We see that lower shear rates generate a higher final reduced
area. In particular, we observe that the reduce area converges
relatively early when the shear rate is lower than $\chi=0.003$. 
%and has a faster convergence than the high shear rate cases.
Panel (c) shows that the total arc length remains constant for all time
with all four shear rates. Combining the behavior of the reduced area
and the total arc length, the excess length must increase in time and be
larger for higher shear rates as observed in panel (d). In all these
results, there are oscillations that can be explained by the granularity
of the JP vesicle which results in a midplane that is non-smooth.
%Overall the total lengths of the bilayer have the same converging value
%in all test shear rates.

\begin{figure}
\begin{center}
\hspace{-0.6cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{0.6cm}
\includegraphics[height=2in]{DecayRate.eps}\\
\includegraphics[height=2in]{ArcLength.pdf}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) Total arc lengths of the midplanes over
  time for four shear rates. (b) From exponential fits in panel (a), we
  obtain the decay rate $k$ for a number of different shear rates. The
  inset plots the terminal reduced areas. (c) Reduced area transitions
  over time. (d) Excess length of the midplanes. For all panels, a set
  of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in
  simulations. The legend in panel (d) applies to both panels (a) and
  (c).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between two leaflets. When the shear rate is sufficiently large, take
$\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip between a
pair of particles over time. The pair we consider are colored in blue
and yellow. In this series of tests, we compute the mean particle
position and mean angle $\theta(t)$ between the particle relative
positions with respect to the vesicle center. It is clear that the outer
leaflet has larger tangential velocity than the inner leaflet since the
mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon
is consistent with what has been seen in articles in molecular dynamics
simulations.

%
%\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
  at larger shear rates.}
\end{figure}

To calculate the inter-monolayer friction coefficient for the apposing
JP leaflets, we let
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
%
where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot
\sigma \cdot \nnu} \,ds\rangle$ is the time-averaged, tangential force
along the midplane curve $\mathcal{C}_m$. The parameters $\langle
L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve
length and intermonolayer slip velocity respectively.

@@

Table~\ref{table1} provides dimensional friction coefficients $b$ for
several shear rates and the results are in quantitative agreement with
values previously reported in the literature~\cite{sch-vla-mik2010}
and~\cite{denOtter2007}. The coefficients generally lie within the
range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some outliers.
These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and $\dot\gamma =
0.0066$ ns$^{-1}$) correspond to slip velocities that are too low
relative to shear rate (see the green and red curve in Figure
\ref{figure5}: panel (c)). The JP vesicle consists of only 58
particles and so it is not surprising that discrete effects produce
outliers.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the
flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$.
The behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area,
the steady-state shape can be either an symmetric parachute or
an asymmetric slipper~\cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009}.

>>>>

The centroid of the pre-relaxed $58$-body Janus vesicle is initially
placed at the origin and the shear flow with a shear rate $\chi$ is
applied. Figure~\ref{figure3} shows snapshots of the JP vesicle in the
shear flow with a shear rate $\chi=0.0025$. Panels (a) and (b) show the
initial shape obtained from the relaxation run and the deformed
configurations of the JP vesicle at time $t=4000$ are in panels (c) and
(d). The background color in panels (a) and (c) is the strength of the
action of the hydrophobic attraction. Red corresponds to a strong action
while blue is a weak action. The hydrophobic layer clearly has the
strongest action. To demonstrate the tank-treading behavior of the
vesicle, panels (b) and (d) provide the streamlines of the fluid
velocity around the JP vesicle. In panel (d), we can clearly observe the
clockwise tank-treading motion.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
  JP vesicle where the black arrows point in the direction of the
  hydrophobic side of the JP. (b) The particle velocities and
  streamlines of the configuration in (a). The streamlines are plotted
  in the background as solid curves and the red arrows represent the
  particle velocities. (c) The deformed tank-treading JP vesicle at
  $t=4000$. (d) The particle velocities and streamlines of the
  configuration in (c). The background colors in panels (a) and (c)
  represent the strength of the hydrophobic attraction potential. The
  blue regions have the weakest action and the red regions in the
  bilayer have the strongest action.}
\end{figure}
%

To extract additional physical properties of the proposed model, we
compute the total length, reduced area, and excess length of the bilayer
structure. The enclosed area and the total length of the structure are
calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
where $A$ is the area, and $L$ is the total length of the JP vesicle,
and the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
Figure~\ref{figure4} shows these quantities for a JP vesicle suspended
in a shear flow with shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.
Since the starting configuration is nearly circular, the reduced area
decreases from an initial value close to $1$. The smooth curves in panel
(a) are best fits of the exponential model $A^* = a_0 + b_0 \exp(-kt)$.
Panel (b) shows that the decay rate $k$ is independent of the shear rate
for sufficiently large shear rates, and the terminal reduced areas of
each case are shown in the inset. We see that lower shear rates generate
a higher final reduced area. In particular, we observe that the reduce
area converges relatively early when the shear rate is lower than
$\chi=0.003$. 
%and has a faster convergence than the high shear rate cases.
Panel (c) shows that the total arc length remains constant for all time
with all four shear rates. Combining the behavior of the reduced area
and the total arc length, the excess length must increase in time and be
larger for higher shear rates as observed in panel (d). In all these
results, there are oscillations that can be explained by the granularity
of the JP vesicle which results in a midplane that is non-smooth.
%Overall the total lengths of the bilayer have the same converging value
%in all test shear rates.

\begin{figure}
\begin{center}
\hspace{-0.6cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{0.6cm}
\includegraphics[height=2in]{DecayRate.eps}\\
\includegraphics[height=2in]{ArcLength.pdf}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) The reduced area transitioning over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. (b) The decay rate $k$, using the exponential fit
  to the data in panel (a), for a number of shear rates. The inset shows
  the terminal reduced areas. (c) The total arc lengths of the midplanes
  over time for four shear rates. (d) The excess length of the
  midplanes. For all panels, a set of shear rates
  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
  legend in panel (d) applies to both panels (a) and (c).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated JP vesicle allows us to consider inter-monolayer slip
between the two leaflets. When the shear rate is sufficiently large,
take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
between a pair of particles over time. The pair we consider are colored
in blue and yellow. In this series of tests, we compute the mean
particle position and mean angle $\theta(t)$ between the particle
relative positions with respect to the vesicle center. It is clear that
the outer leaflet has larger tangential velocity than the inner leaflet
since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
consistent with what has been seen in articles in molecular dynamics
simulations.
\todo[inline]{Need a reference here}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the JP vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
  for large shear rates.}
\end{figure}

To calculate the inter-monolayer friction coefficient for the apposing
JP leaflets, we let
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
%
where 
\begin{align}
  \langle F\rangle = \left\langle \int_{\mathcal{C}_M} 
    \jump{\ttau \cdot \sigma \cdot \nnu} \,\dif s \right\rangle
\end{align}
is the time-averaged, tangential force along the midplane curve
$\mathcal{C}_m$. The parameters $\langle L\rangle$ and $\langle
U\rangle$ are the time-averaged midplane curve length and intermonolayer
slip velocity, respectively.

@@

Table~\ref{table1} provides dimensional friction coefficients $b$ for
several shear rates and the results are in quantitative agreement with
values previously reported in the literature (\cite{sch-vla-mik2010}
and~\cite{denOtter2007}). The coefficients generally lie within the
range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some outliers.
These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and $\dot\gamma =
0.0066$ ns$^{-1}$) correspond to slip velocities that are too low
relative to the shear rate (see the green and red curve in
Figure~\ref{figure5}(c)). The JP vesicle consists of only 58 particles
and so it is not surprising that discrete effects produce outliers.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$. The
behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area, the
steady-state shape can be either an symmetric parachute or an asymmetric
slipper~\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}.
